Backbone-Store: An API for Automating Local Caching of Web Application Data

### 2012-05-21 paper/paper.tex
further changes to abstract

% vim: set tw=79 ft=tex :
\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}

@@

\begin{abstract}
Efficiently storing web application data in the client's browser was a
challenging task until the recent HTML5 specification. Web applications that
require fetching the same data that has been previously fetched from a server
can see an improved load time by storing this old data in the client's browser,
requiring only the new data to be retrieved from the server. For our project,
we extended Backbone.js to allow a web developer to easily store and reload a
web application's data using the HTML5 localStorage API. We analyze three
simple applications to study the performance characteristics of loading large
documents, medium-sized emails, and small notes from both the local storage on
the client's browser and on the server. We find that local storage performs
faster than loading the same data from the server. This time difference
increases for larger quantities of the same type of item. Since the threshold
for users perceiving lag is about 100 milliseconds, we show that there are
real-world use cases where loading data from a server would cause users to
perceive lag, while loading the same data from localStorage would be perceived
as instantaneous.
\end{abstract}

@@

Note that 1) and 2) are separated by a delay so as not to overlap in
execution and skew the load time.

>>>>

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}

@@

\begin{abstract}
Efficiently storing web application data in the client's browser was a
challenging task until the recent HTML5 specification. With this new local storage spec, Web applications that require re-fetching the same data from a server
can see an improved load time by storing old data in the client's browser,
requiring only the new data to be retrieved from the server. For our project,
we extended Backbone.js to create our own local caching API to help web developers easily store and reload a web application's data using the HTML5 localStorage API. To evaluate the API,  we analyze three simple applications to measure the performance characteristics of loading large
documents, medium-sized emails, and small notes from both the local storage on
the client's browser and from the server. As expected, we find that local storage performs
faster than loading the same data from the server. This time difference
increases for larger quantities of the same type of item, suggesting that local storage become more advantageous as the amount of loaded data increases. Furthermore, given that the threshold
for users perceiving lag is about 100 milliseconds, we show that there are
real-world use cases where loading data from a server would cause users to
perceive lag, while loading the same data from localStorage would be perceived
as instantaneous.
\end{abstract}

@@

Note that Step 1 and 2 are separated by a delay so as not to overlap in
execution and skew the load time.
